---
name: Owais
surname: Raza
position: "Researcher"
pronouns: he/him
address: "Omaha, NE - US"
phone: (206) 349 4773
www: oraza.github.io
email: "ow.raza@hotmail.com"
github: oraza
googlescholar: weiuxRkAAAAJ&hl
linkedin: owraza
orcid: 0000-0002-3410-441X
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
    pandoc_args: ["--pdf-engine=xelatex"]
header-includes:
  - \usepackage{xcolor}  # Required for custom colors
  - \usepackage{fontspec}  # Essential for custom font control
  - \renewcommand{\bodyfont}{\fontspec{Arial Narrow}}  # Main body text
  - \renewcommand{\bodyfontlight}{\fontspec{Arial Narrow}}  # Fixes descriptions in experience/education
  - \renewcommand{\headerfont}{\fontspec{Arial Narrow}}  # Header elements (removed \bfseries)
  - \renewcommand{\footerfont}{\fontspec{Arial Narrow}}  # Footer text
  - \renewcommand{\descriptionstyle}[1]{{\fontsize{10pt}{1em}\bodyfontlight\upshape\color{darktext}#1}}  # Explicitly sets description style
  - \definecolor{myPink}{HTML}{e91d63}  # Your custom highlight color
  - \renewcommand{\descriptionstyle}[1]{\parbox[t]{17cm}{\bodyfontlight\upshape\color{darktext}#1}}
  - \renewcommand{\entrytitlestyle}[1]{\parbox[t]{5cm}{\bodyfont\bfseries\color{darktext}#1}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Summary
\fontspec{Arial Narrow}
\fontsize{10}{1em}
PhD-trained epidemiologist with 15+ years of experience in public health research, teaching, and mentorship. Specializes in \textbf{\textcolor{myPink}{quantitative data analysis}} and \textbf{\textcolor{myPink}{data visualization}} using R, STATA, and SPSS. Background in \textbf{\textcolor{myPink}{spatial epidemiology}}, \textbf{\textcolor{myPink}{maternal and child health}}, and \textbf{\textcolor{myPink}{curriculum development}}. With a strong commitment to \textbf{\textcolor{myPink}{diversity}}, \textbf{\textcolor{myPink}{equity}}, and \textbf{\textcolor{myPink}{inclusion}} through my research and community engagement, I promote \textbf{\textcolor{myPink}{open science}} and embrace a growth mindset, always seeking to learn and apply new methodologies. Beyond my academic achievements, I am a strong proponent of work-life balance and gender equality.



# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D.", "2018", "Tehran University of Medical Sciences", "Tehran, Iran",
  "MBBS", "2006", "Ziauddin University", "Karachi, Pakistan",
) %>%
  detailed_entries(Institution, Where, Degree, Year)
```

# Experience

```{r}
library(tibble)
library(vitae)
tribble(
  ~what, ~when, ~with, ~where, ~details,
  "Research Mentor", "Jul 2024 – Present", "BMY Health, Canada", "Remote",
  list("Conducting data analysis workshops (SPSS and STATA) for internship programs in collaboration with BMY Health (Pakistan).", "Served on the Scientific Review Committee (SRC) and the Research Ethics Board (REB)."),
  
  "Senior Researcher", "Jun 2024 – Present", "BMY Health, Pakistan", "Remote",
  list("Directed the Research Internship Program (Dec 2024 Cohort)",
       "Mentored interns, developed training modules, assessed intern goals, and provided guidance on research project design and execution."),
  
  "Assistant Professor", "Feb 2020 – Jul 2024", "School of Public Health, Dow University of Health Sciences", "Karachi, Pakistan",
  list("Developed public health curricula and taught UG/PG courses in epidemiology, biostatistics, and research methods.",
       "Supervised student research and theses."),
  
  "Deputy Director (Research)", "Nov 2018 – Jan 2020", "PPHI Sindh", "Karachi, Pakistan",
  list("Led research initiatives across 22 districts, using DHIS data to support program monitoring and planning.",
       "Conducted healthcare facility assessment projects and led a warehouse assessment across all 22 districts.",
       "Oversaw key institutional studies, including A Report on Cesarean Section Audit and Warehouse Assessment of PPHI Sindh.",
       "Established the Institutional Review Board (IRB) to ensure ethical research practices across all projects."),
  
  "Teaching Assistant", "Apr 2014 – Sep 2017", "Department of Epidemiology & Biostatistics, Tehran University of Medical Sciences", "Tehran, Iran",
  list("Supervised two rounds of Community Assessment Program as a part of MPH program.",
       "Co-supervised MPH theses",
       "Facilitated research methodology and epidemiology courses, and conducted statistical software workshops (SPSS, STATA, R)."),
  
  "Research Assistant", "May 2013 – Dec 2014", "Non-Communicable Diseases Research Center, Tehran University of Medical Sciences", "Tehran, Iran", 
  list("Coordinated maternal and child health studies.", "Contributed to a national and sub-national burden of disease analysis on maternal conditions in Iran."),
  
  "Lecturer", "Feb 2008 – Sep 2012", "Ziauddin University", "Karachi, Pakistan",
  list("Taught epidemiology and biostatistics moduls.", "Led PBL sessions, supervised student research, and conducted SPSS workshops for medical students.")) %>% 
  detailed_entries(with, where, what, when, details)
```


\newpage

# SKILLS
```{r}
tribble(
  ~Skill, ~Description,
  "R, SPSS, STATA", "Statistical programming, data management, advanced analysis, and visualization.",
  "ArcGIS, GWR, Geospatial Analysis", "Spatial data processing, mapping, and geographic analysis.",
  "Scientific Writing, Data Visualization, Peer Review", "Drafting academic papers, reports, grant proposals, presenting data visually, and reviewing manuscripts for scientific journals.",
  "Project Management, Ethical Review & Compliance, Open Science Practices", "Leading research projects, ensuring ethical standards and IRB compliance, and promoting transparency and reproducibility in research."
) %>%
  detailed_entries(Skill, Description)
  
```
# INVITED TALK:
\color{black}
\fontsize{11pt}{1.5em}
* May 2023 - 1st Family Medicine Research Day: \textbf{\textcolor{myPink}{Fifty Shades of Medical Research}} hosted by Department of Family medicine, Indus Hospital and Health Network.

* Jan 2023 - Quality of Human Resources in Health: \textbf{\textcolor{myPink}{Public Health and Research \& Development (R\&D) Context}} hosted by Ziauddin University.

* Aug 2022 - Moderated Talk for \textbf{\textcolor{myPink}{Ex-Faculty Talk Series: Dr Amir Omair (Ex-faculty member of Department of Community Health Sciences, Ziauddin University)}} hosted by Ziauddin University.

* Dec 2021 - Moderated session at \textbf{\textcolor{myPink}{International Conference on SDGs: Moving Towards Population Health \& Wellbeing}}, organized by Dow University of Health Sciences.

* Dec 2021 - Scientific Session on \textbf{\textcolor{myPink}{Research, Education and The Way Forward: The Good, The Bad \& The Ugly of Medical Research}} hosted by Ziauddin University.

* May 2020 - \textbf{\textcolor{myPink}{COVID Session \# 7: Public Health, Epidemiology \& Clinical Research}} hosted online by Ziauddin Alumni Association.

# Peer Review Activities:
\color{black}
\fontsize{11pt}{1.3em}
* Journal of Health, Population and Nutrition
* International Journal for Equity in Health
* Journal of Current Ophthalmology
* BMC Health Services Research
* PLOS Global Public Health
* Archives of Public Health
* Discover Mental Health
* Discover Public Health
* BMC Public Health
* Scientific Reports
* BMJ Open
* Midwifery
* Heliyon

# Publications
\fontspec{Arial Narrow}
\color{black}
\fontsize{11pt}{1em}
```{r}
library(dplyr)

bibliography_entries("publications.bib") %>%
  arrange(desc(issued))

```






